Defending Against Web Application Attacks: Approaches, Challenges and Implications \newline\newline \small{\textbf{Response to Review Comments}}

### 2016-09-19 docs/comments/comments.tex
minor changes and proofs

{\bf Comment} ``The second and third reviewers
have pointed out problems in missing related work and
descriptions that need to polished.
Please address them carefully in the next revision
for the next round of review."\\

@@

Note that,
most of these mechanisms were not
extensively tested in terms of security.
However,
such solutions do not need to be
established purely through testing,
since they provide systematic
arguments as to why their design is
secure against application attacks.
We stress this issue in Subsection
7.1 (``Improving Testing Accuracy").
Furthermore,
we discuss the usability issues of
{\sc ifc} solutions in Subsection 6.4
(``Ease of Use").

>>>>

{\bf Comment:} ``The second and third reviewers
have pointed out problems in missing related work and
descriptions that need to polished.
Please address them carefully in the next revision
for the next round of review."\\

@@

Note that,
most of these mechanisms were not
extensively tested in terms of security.
However,
such solutions do not need to be
validated purely through testing,
since they provide systematic
arguments as to why their design is
secure against application attacks.
We stress this issue in Subsection
7.1 (``Improving Testing Accuracy").
Furthermore,
we discuss the usability issues of
{\sc ifc} solutions in Subsection 6.4
(``Ease of Use").
